\documentclass[12pt]{book}
\usepackage{amsmath} % AMS Math Package
\usepackage{amsthm} % Theorem Formatting
\usepackage{amssymb}    % Math symbols such as \mathbb
\usepackage{graphicx} % Allows for eps images
\usepackage[dvips,letterpaper,margin=1in,bottom=0.7in]{geometry}
\usepackage{amsfonts,latexsym,amsthm,amssymb,amsmath,amscd,euscript}
\usepackage{framed}
\usepackage{enumitem}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{fullpage}
\usepackage{hyperref}
    \hypersetup{colorlinks=true,citecolor=blue,urlcolor =black,linkbordercolor={1 0 0}}

\newenvironment{statement}[1]{\smallskip\noindent\color{black}{\bf #1.}}{}
\allowdisplaybreaks[1]
%Below are the theorem, definition, example, lemma, etc. body types.

\newtheorem{theorem}{Theorem}
\newtheorem*{proposition}{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{postulate}[theorem]{Postulate}
\theoremstyle{definition}
\newtheorem{defn}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{notation}{Notation}
\newtheorem*{note}{Note}

% You can define new commands to make your life easier.
\newcommand{\BR}{\mathbb R}
\newcommand{\BC}{\mathbb C}
\newcommand{\BF}{\mathbb F}
\newcommand{\BQ}{\mathbb Q}
\newcommand{\BZ}{\mathbb Z}
\newcommand{\BN}{\mathbb N}
\newcommand{\Sq}{\mathrm{Sq}}
\newcommand{\mt}{\mathcal{T}}
\newcommand{\mo}{\mathcal{O}}
\newcommand{\p}{\partial}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\ms}{\mathcal{S}}
\newcommand{\id}{\mathrm{id}}
\newcommand{\seq}{\subseteq}
\newcommand{\s}{\subset}
\newcommand{\dint}{\displaystyle\int}
\DeclareRobustCommand{\rchi}{{\mathpalette\irchi\relax}}
\newcommand{\irchi}[2]{\raisebox{\depth}{$#1\chi$}}
% We can even define a new command for \newcommand!
\newcommand{\nc}{\newcommand}
\renewcommand\qedsymbol{$\blacksquare$}
\let\oldemptyset\emptyset
\let\emptyset\varnothing
\usepackage{scalerel}
\let\lctau\tau % save the lowercase of '\tau'
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\renewcommand{\tau}{\scalerel*{\lctau}{X}}
\usepackage{times}
\usepackage{textcomp}
\begin{document}
\begin{center}
\textbf{\Large Chern Classes}
\end{center}

Chern classes are important characteristic classes in geometry and topology. They are similar to Stiefel-Whitney classes to some extent, but they are defined for complex vector bundles and integer cohomology. Now, to formally define Chern classes, let $\pi : E \to B$ be a complex vector bundle and $E_{0}$ be $E$ with the image of the zero section removed. Next, fix a Hermitian metric on $E$, and define a new vector bundle over $E_{0}$ by letting the fiber be the orthogonal complement under the chosen metric. Call this new bundle $E'.$

We can now finally define Chern classes. Chern classes are elements $c_{i}(E) \in H^{2i}(B;\BZ)$, which are defined inductively. If $E$ has rank $n$, then $c_{n}(E) = e(E)$, where $e(E)$ is understood to be the Euler class of $E$ considered as a real vector bundle. Then, for $i < n$, $c_{i}(E) = (\pi_{0}^{*})^{-1}c_{i}(E')$, where $\pi_{0} : E_{0} \to B.$ Finally, $c_{i}(E) = 0$ if $i > n.$

Some consequences of this definition include that the Chern classes are natural, $c(E_{1} \oplus E_{2}) = c(E_{1})$ if $E_{2}$ is trivial, and $c(E_{1} \oplus E_{2}) = c(E_{1}) \smile c(E_{2})$, where $c(E) = \sum c_{j}(E)$. Note also that there are two other definitions of Chern classes that are commonly used. The first is similar to the axiomatic definition of Stiefel-Whitney classes, and the second is defined through Chern-Weil theory.

Now we discuss the Chern-Weil theory approach. Fix a connection on $E$, and let $F$ be the curvature of this connection. We can write $\det(\id + A) = 1 + P_{1}(A) + \ldots + P_{n}(A)$, where $P_{j}$ are degree $j$ homogeneous polynomials. Then, define $c_{j}(E) = [P_{j}(\frac{i}{2\pi}F)] \in H^{2j}(B;\BZ).$ The fact that these classes are integral requires a bit of justification, but this definition turns out to be equivalent to the other definitions.
\end{document}